
\section*{Acknowledgements}
    Firstly, I want to extend my deepest gratitude to my mentors, Prof. Yasmine Sassa and Prof. Martin Månsson for guiding me through this project. Without Yasmine, my understanding of solid state physics would still be close to zero and I would never have been able to finish this project. The feedback she provided for my early draft has been a huge help in guiding this report to its final form. I would also like to thank my research partner Yujing Jiang. Despite our projects taking quite different turns, it has nevertheless been a joy to embark on this journey with her. 
    %Moreover, I would like to thank [THE PHD STUDENTS TOR AND ADHIATY(?)] for guiding me through the lab on my first few days of the mentorship and helping me understand what and how the equipment worked. 
    Additionally, I would like to thank Jakob Hüttner, Gustav Dargin, Hanna Åkerman, Carl Viggo Nilsson Gravenhorst-Lövenstierne, and 
    Daniel Nordström for taking the time to read through my report and ensure that it could reach its highest potential. I also want to extend thanks to the organizers of Rays for putting in all their energy to make sure that this years edition was the best it could be.
    Finally, I would like to thank Europaskolan Strängnäs, Wallenbergs Stiftelse, Särskilda fonden and Rays --- for Excellence for making all of this possible.
    %Not good, needs improvements
    %Thank Europaskolan Strängnäs and Jacob Wallenbergs Stiftelse, Särskilda fonden
    
    %People who have read my report: Gustav Dargin, Jakob Hüttner, Yasmine Sassa, Hanna Åkerman, Carl Viggo Nilsson Gravenhorst-Lövenstierne